%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{soul}
\usepackage{tikz}
\usepackage{tabto}
\usepackage{multicol}
\usepackage{lastpage}
\setlength{\multicolsep}{-3.0pt}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheadingSingle}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\ExternalLink}{%
    \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{%
        \begin{scope}[x=1ex, y=1ex]
            \clip (-0.1,-0.1)
                --++ (-0, 1.2)
                --++ (0.6, 0)
                --++ (0, -0.6)
                --++ (0.6, 0)
                --++ (0, -1);
            \path[draw,
                line width = 0.5,
                rounded corners=0.5]
                (0,0) rectangle (1,1);
        \end{scope}
        \path[draw, line width = 0.5] (0.5, 0.5)
            -- (1, 1);
        \path[draw, line width = 0.5] (0.6, 1)
            -- (1, 1) -- (1, 0.6);
        }
    }

% control printing parts of text e.g. improvement reason to explain in interview etc.
\newif\ifprintstuff
\printstufffalse
% \printstufftrue

% makes strikethrough from soul lib optional with wrapper custom command
\providecommand{\opst}[1]{\ifprintstuff\st{#1}\else\fi}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%----------HEADER-----------------
\fancyhead[C]{\tabto{3cm} \href{https://addyzbio.github.io}{\scriptsize \underline{Latest Resume {\ExternalLink}}}}

%-----------FOOTER-----------------
\lfoot{\scriptsize publish date: \today}
\cfoot{\tabto{3cm} \scriptsize version: 3.0}
\rfoot{\scriptsize page \thepage of \pageref{LastPage}}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Aditya Thakur} & \opst{+91-0123456789}\\
  Software Engineer with over 7 years of experience & \href{mailto:engg.aditya.thakur@gmail.com}{engg.aditya.thakur@gmail.com}\\
  Nagarro Software Pvt. Ltd. & \href{https://github.com/orgs/contrib-src-openly/repositories}{\underline{GitHub Contributions {\ExternalLink}}} \href{https://www.linkedin.com/in/-aditya-thakur-/}{\underline{LinkedIn {\ExternalLink}}}\\
\end{tabular*}
\linebreak

Seasoned Java Backend and DevOps Platform Engineer seeking opportunities to apply strong technical expertise and emerging AI skills to build robust and scalable applications.

%-----------SKILLS-----------------
\section{Skills}
\begin{multicols}{2}
  \resumeSubHeadingListStart
    \resumeItem{Languages/Frameworks/Libraries}
      {Java, Spring Boot, Spring Cloud, Spring Security, Spring WebFlux, Reactive with Mono/Flux and Mutiny (Uni/Multi), WebClient, RestTemplate, Feign Client, AOP, Quarkus native, JWT/OAuth2, MapStruct, Jackson, Gson, Lombok, Log4j/Slf4j, Micrometer, OpenTelemetry, Shell (Bash), JavaScript/TypeScript, SQL, Python, NodeJS, ReactJS}
    \resumeItem{Architecture}
      {Microservices Architecture, Event-Driven Architecture, Distributed Systems, REST APIs, API-first, Design Patterns, SOLID Principles, Distributed Observability with centralized logging and tracing}
    \resumeItem{Messaging and Streaming}
      {Apache Kafka (Producers, Consumers, Streams, Connectors), Debezium CDC}
    \resumeItem{Persistence, Search and Caching}
      {JPA/Hibernate, Panache, PostgreSQL, MySQL, Oracle SQL, Aurora DB, MongoDB, Redis/Valkey Cache, Flyway}
    \resumeItem{Developer Tools}
      {IntelliJ IDEA, VS Code, STS, Git, Maven, Gradle, SonarQube, Postman, DBeaver, pgAdmin, Atlassian Jira, ServiceNow, GraalVM}
    \resumeItem{DevOps and Cloud}
      {GitHub Actions, Docker, Kubernetes, Helm Charts, KEDA, AWS (EKS, ECR, S3, RDS, CodePipeline, CodeBuild, Secrets Manager, CDK), Jenkins, GCP (GKE, Compute Engine)}
    \resumeItem{Tools/Platforms}
      {Git, ArgoCD, Prisma Cloud Compute, Istio Service Mesh, Terraform, Backstage}
    \resumeItem{Observability and Performance}
      {Grafana, Prometheus, Splunk, Dynatrace, Kibana, VictorOps, Distributed Tracing, JMeter, Profiling and Performance Tuning}
    \resumeItem{AI-Assisted Development and Automation}
      {Prompt Engineering, AI Code Migration, Developer Automation, RAG Architecture, Vector Databases, AI Tools (ChatGPT, Claude, GitHub Copilot, Amazon Bedrock)}
    \resumeItem{Testing and Documentation}
      {JUnit, Mockito, Swagger UI/OpenAPI, Performance Testing with K6, Contract Testing with Microcks, mkdocs, Atlassian Confluence}
    \resumeItem{Data Formats and Standards}
      {JSON, YAML, XML, AVRO, OpenAPI Specification, Markdown, HTML}
    \resumeItem{Domain Experience}
      {Fintech Financial Systems, E-Commerce and Retail}
    \resumeItem{HomeLab and AI/ML}
      {IoT, Home Automation with HomeAssistant, Proxmox, LLM, Ollama, Gradio, ComfyUI, n8n}
  \resumeSubHeadingListEnd
\end{multicols}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Nagarro - Digital Product Engineering Platform}{Remote, Jul. 2021 - Present}
      {Platform Engineering, CRM - Associate Staff Engineer}{Java 21, Gradle, Docker, Eventing, AWS, AI}
      \resumeItemListStart
        \resumeItem{Multi-tenant Microservices, Frameworks and Build Plugins}
          {Produced production-grade observability, security, database and Kafka starter libraries ensuring comprehensive system functionality and increased development efficiency.
          Developed plugins for OpenAPI and AsyncAPI/AVRO specifications, facilitating code generation and scaffolding with Projen. Used by over \underline{100 microservices} for rapid API-first development.}
        \resumeItem{Event-driven}
          {Designed and established loosely coupled distributed systems using Spring Boot, Quarkus (Native), Apache Kafka, and Debezium (CDC) for real-time data streaming and high throughput processing.
          Owned Enterprise-grade notification service utilizing Kafka connectors.}
        \resumeItem{Cross-cutting DevOps and Security concerns}
          {Created and improved Docker base images with \underline{58\% size reduction} and \underline{43\% reduction in security vulnerabilities}\opst{ using distroless and updated spring boot framework and java versions}. Used capabilities like multi-stage and multi-arch for increased efficiency.
          Strengthened security with GitHub Actions checks like SonarQube and established a robust tagging and versioning flow. Achieved \underline{80\% and 33\% run time reduction} respectively in checkstyle\opst{ by skipping compilation, removing task dependencies} and other checks\opst{ by checking git-diff, using setup-gradle action and github actions cache and gradle tasks management by declaring task dependencies and inputs/outputs}.}
        \resumeItem{Cost and performance optimization with AI/MLOps}
          {Prepared AI agents and MCP Servers with Amazon Bedrock, Amazon SageMaker and Claude to migrate from Spring Boot 3 to Quarkus 3 (native) with performance test metrics showing \underline{over 150\% throughput improvement\opst{from (tuned SB) 120 RPS to (untuned Q) 300 RPS with 500m CPU and 512MiB Memory (Q needs 1/10 of SB) by K6}} or 50\% reduced resource consumption and \underline{86\% reduced Docker image size\opst{ ~35MB versus ~250MB}}.}
        \resumeItem{Cloud Automation and SRE}
          {Provisioned infrastructure with \underline{AWS CDK} constructs in TypeScript to manage CloudFormation templates and CI/CD pipelines in \underline{Bash script}; Deployed services with \underline{Helm Charts and ChartMuseum}; System monitoring, alerting and troubleshooting with tools like Splunk, Dynatrace, Grafana, Tempo and Prometheus.}
        \resumeItem{Migration}
          {Assisted in the transition from\opst{ Hybris} monolith to microservice architecture, enhancing scalability with 20\% reduction in time-to-market.}
        \resumeItem{E-commerce and CRM Development}
          {Designed and developed a revamped e-commerce platform and CRM gateway, improving user experience and system efficiency.}
        \resumeItem{CRM Gateway Request Processing}
          {Accepted, processed and routed Account and Appointment bookings from different sources with query and mutation. GraphQL, Netflix DGS library, CRUD, Agile}
        \resumeItem{Tool Integration}
          {Integrated with external tools like Salesforce, Exponea and LeadSquared.}
        \opst{\resumeItem{Highlights}
          {Cross-functional, smart, modular, scalable and well-documented.}}
      \resumeItemListEnd

    \resumeSubheading
      {Verifone India Pvt. Ltd. - A Payment Gateway Company}{Bangalore, Mar. 2019 - June 2021}
      {Microservices Orchestrator and Payment Processors - SDE}{Java 11, Spring Boot 2, Tomcat, Maven}
      \resumeItemListStart
        \resumeItem{Workflow Definition}
          {Created a fully flexible structure to define microservices workflow customized for multiple markets using Spring Beans, Spring Async, and Spring Retry to handle exceptions and send custom responses.}
        \resumeItem{JSON and HEX}
          {Translated JSON from Terminal/POS payment devices into Acquirer-specific HEX requests and response back to JSON. Java 8, OOP principles, SOLID design}
        \resumeItem{FOREX Integration}
          {Communicated with FOREX Rate processing provider over HTTP using REST and JSON.}
        \resumeItem{Code Development and Repository Management}
          {Spearheaded code development, configuration, and administration of Bitbucket repositories and Jenkins jobs.}
        \resumeItem{Performance Optimization}
          {Achieved a \underline{90\% reduction in execution time} through custom benchmarking\opst{ of different JSON libraries and MapStruct vs ModelMapper} using Java Microbenchmarking Harness (JMH).}
        \resumeItem{Project Deliveries}
          {Delivered critical payment domain projects for both internal stakeholders and international clients, ensuring high standards of quality and timeliness.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {PG-DAC, ACTS}{Pune}
      {Java Developer}{Aug. 2018 - Feb. 2019}
      \resumeItemListStart
        \resumeItem{Web Application Development}
          {Implemented a web app for student-faculty interaction within a month.}
      \resumeItemListEnd

    \resumeSubheading
      {AndroAddyct}{Remote}
      {Android App Development Freelancer}{May 2016 - Dec. 2016}
      \resumeItemListStart
        \resumeItem{Application Lifecycle Management}
          {Managed the application lifecycle having about \underline{900 active user devices} across \underline{175 countries/regions}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------ACCOLADES-----------------
\section{Accolades, Recognition and Certifications}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Nagarro}{}
      {Review and Feedback}{}
      \resumeItemListStart
        \resumeItem{2025}
          {Engineering Excellence Award}
        \resumeItem{Consistent}
          {Extraordinary Role Model, Highly Valuable feedback}
      \resumeItemListEnd
    \resumeSubheading
      {Udemy}{}
      {Certifications}{}
      \resumeItemListStart
        \resumeItem{AI/ML}
          {Completed Training on LLM Engineering, Generative AI, Agentic AI Engineer and AI Engineer Production Track}
        \resumeItem{DevOps}
          {Kubernetes, Docker, Git}
        \resumeItem{JavaScript}
          {NodeJS, ReactJS}
      \resumeItemListEnd
    \resumeSubheading
      {KodeKloud}{}
      {Certifications}{}
      \resumeItemListStart
        \resumeItem{AWS}
          {Basics, ECS}
        \resumeItem{DevOps}
          {Kubernetes}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
   $\bullet$ PG-DAC from CDAC-ACTS, Pune, MH (79.25\%) & $\bullet$ B.E. from MIET(RTMNU), Gondia, MH (78.80\%)\\
\end{tabular*}
% \section{Education}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {PG-DAC (Post Graduate Diploma in Advanced Computing)}{79.25\%}
%       {CDAC ACTS}{Pune, MH}
%     \resumeSubheading
%       {B.E. (Bachelor of Engineering)}{78.80\%}
%       {MIET(RTMNU)}{Gondia, MH}
%   \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}